DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-29 ase2017/paper.tex

%---------------------------------------------------
\subsection{Benchmarks Description}
%---------------------------------------------------

@@

>>>>

%---------------------------------------------------
\subsection{Benchmarks Description}
\label{benchmarks-description}
%---------------------------------------------------

@@

The main purpose of our experiments for set of the benchmarks described in Section~\ref{benchmarks-description} is (1) evaluate the performance of the \tool to produce stable controllers, and also (2) confirm the
stability of the synthesized controllers outside of our model in state-space and transfer-function formats.
